\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-03 paper.tex

To solve this problem and open up the peerless beauty of the Golden Pavilion to
more people, our team created ARuko and Editour. These two tools comprise a
complete platform for designing and experiencing AR-enhanced tours. Editour
makes it easy to design custom audio tours including audio, text, and images,
while ARuko allows users to seamlessly experience historic sites in an intuitive
and novel way. Many AR apps require specific markers, like the those shown in
Figure~\ref{fig:arMarker}. Too avoid needing to place any physical object that
would disturb the buildings or grounds of a historic site our app does not rely
on these markers. Instead, our ARuko recognizes images of objects that are
already at the site, and uses them to display informative AR pop-ups. See
Sections~\ref{sec:translationFeature} and \ref{sec:mapOverlayFeature} for
more details.

@@

Most existing applications using AR, in our team's opinions, do not leverage the
full potential of this emerging technology. As with any new field, our
understanding of AR and how to develop for it is limited. All sorts of different
challenges and limitations face the development and production of AR apps. Here
are some that we considered when working on our app.

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. Many AR apps and features available on smartphones offer
very little in the way of functionality or practicality; quite simply, they
primarily primarily revolve around deploying
gimmicks~\autocite{theappsolutions2018}. For example, one of the most popular
apps to use AR, \textit{Pokémon Go}, primarily uses its AR feature to place a
Pokémon on top of a camera's video feed. Disappointingly, it does not interact
with anything around it. It just floats a fixed distance away from the user.

@@

While not a disaster, we had some initial trouble getting started with Unity.
Different versions of Unity do not play well with each other, and it often runs
into bugs on older hardware, such as the laptops we had to work with.
Furthermore, a stable version of the Unity editor is not available on
GNU/Linux~\autocite{best2019}, so one of our team members had to install macOS
in order to use it. We were able to resolve these issues in the first weeks of
the project, but it consumed some of our valuable time in July.

>>>>

To solve this problem and open up the peerless beauty of the Golden Pavilion to
more people, our team created ARuko and Editour. These two tools comprise a
complete platform for designing and experiencing AR-enhanced tours. Editour
makes it easy to design custom audio tours including audio, text, and images,
while ARuko allows users to seamlessly experience historic sites in an intuitive
and novel way. Many AR apps require specific markers, like the those shown in
Figure~\ref{fig:arMarker}. Too avoid needing to place any physical object that
would disturb the buildings or grounds of a historic site our app does not rely
on these markers. Instead, ARuko recognizes images of objects that are already
at the site, and uses them to display informative AR pop-ups. See
Sections~\ref{sec:translationFeature} and \ref{sec:mapOverlayFeature} for more
details.

@@

Most existing applications using AR, in our team's opinions, do not leverage the
full potential of this emerging technology. As with any new field, our
understanding of AR and how to develop for it is limited. All sorts of different
challenges and limitations face the development and production of AR apps. In
this section we discuss some of the challenges we faced when working on our app.

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. Many AR apps and features available on smartphones offer
very little in the way of functionality or practicality; quite simply, they
primarily revolve around deploying gimmicks~\autocite{theappsolutions2018}. For
example, one of the most popular apps to use AR, \textit{Pokémon Go}, primarily
uses its AR feature to place a Pokémon on top of a camera's video feed.
Disappointingly, it does not interact with anything around it. It just floats a
fixed distance away from the user.

@@

We had some initial trouble getting started with Unity. Different versions of
Unity do not play well with each other. As a result, we often ran into bugs on
older hardware, such as the laptops we had to work with. Furthermore, a stable
version of the Unity editor is not available on GNU/Linux~\autocite{best2019},
so one of our team members had to install macOS in order to use it. We were able
to resolve these issues in the first weeks of the project, but it consumed some
of our valuable time in July.
